Towards semantic-rich word embeddings

### 2019-03-27 paper/main.tex
Shorten related work section

Typically, there are two kinds of approach for Word Sense Disambiguation (WSD): supervised, which make use of sense-annotated training data, and knowledge-based, which make use of the properties of lexical resources.
%In supervised approach, the most widely used training corpus used is SemCor\cite{semcor}, with 226,036 sense annotations from 352 manually annotated documents.
Knowledge-based systems usually exploit WordNet\cite{wordnet} or BabelNet\cite{babelnet} as semantic network.
%Our solution joins two approaches. We use the knowledge-based word embeddings like GloVe\cite{GloVe} as a baseline for our method and then optimize them in supervised fashion.

The most usual baseline is the Most Frequent Sense\cite{evalmfs} (MFS) heuristic, which selects for each target word the most frequent sense in the training data.
Recent growth of sequence learning techniques using artificial neural networks contributed to WSD research: Raganato et al.\cite{neuralseqmodelingforWSD} propose a series of end-to-end neural architectures directly tailored to the task, from bidirectional Long Short-Term Memory (LSTM) to encoder-decoder models.
Melamud et al.\cite{context2vec} also use bidirectional LSTM it their work. They use large plain text corpora to learn a neural model that embeds entire sentential contexts and target words in the same low-dimensional space, which is optimized to reflect inter-dependencies between targets and their entire sentential context as a whole.

Iacobacci et al.\cite{embeddingsforWSD} were first to try to use word embeddings for WSD. They consider four different strategies for integrating a pre-trained word embeddings as context representation in a supervised WSD system: concatenation, average, fractional and exponential decay of the vectors of the words surrounding a target word.
Peters et al.\cite{deepcontext} create word representations that differ from traditional word embeddings in that each token is assigned a representation that is a function of the entire input sentence. They use vectors derived from a bidirectional LSTM that is trained with a coupled language model objective on a large text corpus.

>>>>

Iacobacci et al.\cite{embeddingsforWSD} were the first to try to use word embeddings for Word Sense Disambiguation.
They consider four different strategies for integrating a pre-trained word embeddings as context representation in a supervised WSD system: concatenation, average, fractional and exponential decay of the vectors of the words surrounding a target word.
Peters et al.\cite{deepcontext} create word representations that differ from traditional word embeddings in that each token is assigned a representation that is a function of the entire input sentence. They use vectors derived from a bidirectional LSTM that is trained with a coupled language model objective on a large text corpus.

The most usual baseline for WSD task is the Most Frequent Sense\cite{evalmfs} (MFS) heuristic, which selects for each target word the most frequent sense in the training data.
Recent growth of sequence learning techniques using artificial neural networks contributed to WSD research: Raganato et al.\cite{neuralseqmodelingforWSD} propose a series of end-to-end neural architectures directly tailored to the task, from bidirectional Long Short-Term Memory (LSTM) to encoder-decoder models.
Melamud et al.\cite{context2vec} also use bidirectional LSTM it their work. They use large plain text corpora to learn a neural model that embeds entire sentential contexts and target words in the same low-dimensional space, which is optimized to reflect inter-dependencies between targets and their entire sentential context as a whole.

%Typically, there are two kinds of approach for Word Sense Disambiguation (WSD): supervised, which make use of sense-annotated training data, and knowledge-based, which make use of the properties of lexical resources.
%In supervised approach, the most widely used training corpus used is SemCor\cite{semcor}, with 226,036 sense annotations from 352 manually annotated documents.
%Knowledge-based systems usually exploit WordNet\cite{wordnet} or BabelNet\cite{babelnet} as semantic network.
%Our solution joins two approaches. We use the knowledge-based word embeddings like GloVe\cite{GloVe} as a baseline for our method and then optimize them in supervised fashion.
